\textls[-15]{\thetitle \mbox{(Technical Report)}}

### 2022-11-08 introduction.tex
fix broken refs

\item We capture the essence of the new language mechanism formally by extending
Martin–Löf type theory with family polymorphism and extensible inductive
types (\cref{sec:metatheory}).
We derive foundational meta\-theoretical results including consistency
and canonicity.
%\EDJ{I will suggest use ``foundational'' instead. Sterling at some places say canonicity is the most basic meta-theoretical property.}
We also formalize the translation implemented by the Coq plugin.

\item We present case studies of using our Coq plugin to mechanize
language metatheories (\cref{sec:coqexample}).
They show how our language design naturally solves the EP and
enables a high degree of reuse and extensibility
for proof engineering.

>>>>

\item We capture the essence of the new language mechanism formally by extending
Martin–Löf type theory with family polymorphism and extensible inductive
types (\cref{sec:metatheory2}).
We derive foundational meta\-theoretical results including consistency
and canonicity.
%\EDJ{I will suggest use ``foundational'' instead. Sterling at some places say canonicity is the most basic meta-theoretical property.}
We also formalize the translation implemented by the Coq plugin.

\item We present case studies of using our Coq plugin to mechanize
language metatheories (\cref{sec:casestudies}).
They show how our language design naturally solves the EP and
enables a high degree of reuse and extensibility
for proof engineering.
